Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex
Therefore

@@

\SubSection{Problem Statement}
The purpose of this paper is therefore to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.

@@

\SubSection{Motivation for Research}
Performing this study would therefore be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.

@@

\Section{Case Company Description}
TBA
\newpage

@@

\Section{References}
Make real ref list later

>>>>

Give a clear introduction to what we mean by different paradigms. Just introduce manual/mdsd and the difference.

@@

\SubSection{Problem Statement}
The purpose of this paper is therefore (XXX probably shouldn't use therefore to refer to the prev section.) to determine whether an organisation's development paradigm should be the basis for deciding which process and design changes to adopt.

@@

\SubSection{Motivation for Research}
Performing this study would therefore (XXX same) be an attempt at filling in a gap in literature. Academia would be interested in this for its own merit or, most likely, as a stepping stone towards further research.

@@

\Section{Case Company Description}
TBA

@@

\bibliographystyle{latex8}
\bibliography{latex8}
